### 2017-09-26 Sections/abstract.tex
Minor updates. Author update
master text from Tim Byrnes - not edited in
minor

\begin{abstract}
\includegraphics[width=0.75\columnwidth]{sketch_cover}
\newpage
The desire to share and unite remote digital assets motivated the development of the classical internet, the enabler of the entire 21st century economy and our modern way of life. As we enter the quantum era, it is to be expected there will be a similar demand for networking quantum assets, motivating a \textit{global quantum internet} for bringing together the world's quantum resources, leveraging off their exponential trajectory in capability. We present models for quantum networking, how they might be applied in the future, and the implications they will have. Socially, economically, politically and geo-strategically, the upcoming era of quantum supremacy will be as significant for the 21st century as the transistor was for the 20th.
\\[4pt]
The inherently different scaling in the computational power of quantum computers fundamentally changes the dynamics of how they will operate in the future. Given their high expected initial cost, a client/server model for outsourcing computation will be essential for enabling the accessibility and proliferation of this technology, and ensuring its economic viability. We therefore anticipate the emergence of \textit{cloud quantum computing}, a model for outsourcing quantum computations to the network. We argue that economic efficiency will mandate that all future quantum computers be united into a single global \textit{virtual quantum computer}, offering exponentially more power to all network participants than if they were to keep their resources to themselves. This model for the allocation of computational resources is uniquely quantum, with no classical analogue, completely altering the economic landscape for the future of computation.
\\[4pt]
Given the sensitivity of much of the data to which future quantum computers are going to foreseeably be applied, protocols for encrypted quantum computation will be essential -- the outsourcing of computations that neither an eavesdropper nor even the server performing the computation can spy on. This will enable new models for the commercialisation and proliferation of quantum technologies, unlike any existing models for classical computing.
\\[4pt]
We argue that the quantum internet will not create a system of winners and losers, but will rather be of benefit to all of humanity, rich and poor alike, to an even greater extent than the classical internet. It is therefore essential that it be imminently established and pursued.
\\[4pt]
While this work is only an early step in a rapidly developing field, still in its infancy, the central concepts we present will be highly relevant to future developments, laying the groundwork for this blossoming field.
\\[4pt]
We present both original ideas, as well as an extensive review of relevant and related background material. The work is divided into technical sections (requiring only a basic knowledge of the notation of quantum mechanics), for those interested in mathematical details, as well as extensive, entirely non-technical sections for the less technically inclined.
\\[4pt]
We target this work very broadly at quantum and classical computer scientists, classical computer systems, software and network engineers, physicists, economists, artists, and those just generally curious about the future of quantum technologies and what they might bring to humanity.
\\[4pt]
\textit{--- Ad astra per alas fideles. Scientia potentia est.}
\newpage
\end{abstract}

>>>>

\begin{abstract}
\newpage
The desire to share and unite remote digital assets motivated the development of the classical internet, the enabler of the entire 21st century economy and our modern way of life. As we enter the quantum era, it is to be expected there will be a similar demand for networking quantum assets, motivating a \textit{global quantum internet} for bringing together the world's quantum resources, leveraging off their exponential trajectory in capability. We present models for quantum networking, how they might be applied in the future, and the implications they will have. Socially, economically, politically and geo-strategically, the upcoming era of quantum supremacy will be as significant for the 21st century as the transistor was for the 20th.
\\[4pt]
The inherently different scaling in the computational power of quantum computers fundamentally changes the dynamics of how they will operate in the future. Given their high expected initial cost, a client/server model for outsourcing computation will be essential for enabling the accessibility and proliferation of this technology, and ensuring its economic viability. We therefore anticipate the emergence of \textit{cloud quantum computing}, a model for outsourcing quantum computations to the network. We argue that economic efficiency will mandate that all future quantum computers be united into a single global \textit{virtual quantum computer}, offering exponentially more power to all network participants than if they were to keep their resources to themselves. This model for the allocation of computational resources is uniquely quantum, with no classical analogue, completely altering the economic landscape for the future of computation.
\\[4pt]
Given the sensitivity of much of the data to which future quantum computers are going to foreseeably be applied, protocols for encrypted quantum computation will be essential -- the outsourcing of computations that neither an eavesdropper nor even the server performing the computation can spy on. This will enable new models for the commercialisation and proliferation of quantum technologies, unlike any existing models for classical computing.
\\[4pt]
We argue that the quantum internet will not create a system of winners and losers, but will rather be of benefit to all of humanity, rich and poor alike, to an even greater extent than the classical internet. It is therefore essential that it be imminently established and pursued.
\\[4pt]
While this work is only an early step in a rapidly developing field, still in its infancy, the central concepts we present will be highly relevant to future developments, laying the groundwork for this blossoming field.
\\[4pt]
We present both original ideas, as well as an extensive review of relevant and related background material. The work is divided into technical sections (requiring only a basic knowledge of the notation of quantum mechanics), for those interested in mathematical details, as well as extensive, entirely non-technical sections for the less technically inclined.
\\[4pt]
We target this work very broadly at quantum and classical computer scientists, classical computer systems, software and network engineers, physicists, economists, artists, musicians, and those just generally curious about the future of quantum technologies and what they might bring to humanity.
\\[4pt]
\textit{--- Ad astra per alas fideles. Scientia potentia est.}

\includegraphics[width=0.55\columnwidth]{sketch_cover}
\newpage
\end{abstract}

### 2017-09-26 Sections/classical_networking_protocols.tex
minor

In the Ethernet protocol, every user is free to broadcast data onto the shared channel as they please -- all users transmit to, and receive from a single shared channel. However, clearly sometimes packet `collisions' will occur\index{Collision handling}, resulting in packet corruption. To overcome this, Ethernet packets contain a checksum that can be used to verify upon arrival whether a packet has been corrupted by a collision. If a collision is detected, the respective users are able to re-broadcast, following a randomly chosen waiting period (known as `backoff')\index{Backoff}. Collisions therefore reduce network performance, and it follows that network bandwidth decreases with the number of users competing for bandwidth\footnote{Think of that awkward dinner table conversation, where two people start talking simultaneously. It's immediately obvious to them both that they are interfering with one another, and if they were to just talk over one another (packet collision), no one would understand either of them. So, they both awkwardly pause, before starting to speak again. In a \textit{really} awkward conversation, they will both start again simultaneously, after which there will be an even longer awkward pause before recommencing. Eventually, this self-regulating system will resolve itself probabilistically, with a sole victor controlling the airwaves, commanding the attention of the listeners. Provided that all dinner guests adhere to social etiquette and backoff appropriately, with repeated conversations, all guests will statistically receive an equitable share of attention, albeit with some wastage of conversation time owing to the periods of silence. Clearly, the proportion of the time wasted due to collisions will scale up with the number of guests, limiting the protocol to not-too-large tables (or very quiet guests).}.

>>>>

In the Ethernet protocol, every user is free to broadcast data onto the shared channel as they please -- all users transmit to, and receive from a single shared channel. However, clearly sometimes packet `collisions' will occur\index{Collision handling}, resulting in packet corruption. To overcome this, Ethernet packets contain a checksum that can be used to verify upon arrival whether a packet has been corrupted by a collision. If a collision is detected, the respective users are able to re-broadcast, following a randomly chosen waiting period (known as `backoff')\index{Backoff}. Collisions therefore reduce network performance, and it follows that network bandwidth decreases with the number of users competing for bandwidth\footnote{Think of that awkward dinner table conversation, where two people start talking simultaneously (Peter \& Jon). It's immediately obvious to them both that they are interfering with one another, and if they were to just talk over one another (packet collision), no one would understand either of them. So, they both awkwardly pause, before starting to speak again. In a \textit{really} awkward conversation, they will both start again simultaneously, after which there will be an even longer awkward pause before recommencing. Eventually, this self-regulating system will resolve itself probabilistically, with a sole victor controlling the airwaves, commanding the attention of the listeners. Provided that all dinner guests adhere to social etiquette and backoff appropriately, with repeated conversations, all guests will statistically receive an equitable share of attention, albeit with some wastage of conversation time owing to the periods of silence. Clearly, the proportion of the time wasted due to collisions will scale up with the number of guests, limiting the protocol to not-too-large tables (or very quiet guests).}.

### 2017-09-26 Sections/foreword.tex
minor

Quantum technologies\index{Quantum technologies} are not just of interest to quantum physicists, but will have transformative effects across countless areas -- the next technological revolution. For this reason, this work is directed at a general audience of not only quantum computer scientists, but also classical computer scientists, physicists, economists, artists, and computer, software and network engineers. More broadly, we hope this work will be of interest to those who recognise the future significance of quantum technologies, and the implications (or even just curiosities) that globally networking them might have. We expect the answer to that question will look very different to what emerged from the classical internet.

@@

>>>>

Quantum technologies\index{Quantum technologies} are not just of interest to quantum physicists, but will have transformative effects across countless areas -- the next technological revolution. For this reason, this work is directed at a general audience of not only quantum computer scientists, but also classical computer scientists, physicists, economists, artists, musicians, and computer, software and network engineers. More broadly, we hope this work will be of interest to those who recognise the future significance of quantum technologies, and the implications (or even just curiosities) that globally networking them might have. We expect the answer to that question will look very different to what emerged from the classical internet.

@@

The theme music for this work may be found \href{http://soundcloud.com/peter-rohde/wir-sind-ein-volk}{here}\index{Theme music}.
